Signal Processing for Broadcast FM Radio Demodulation

### 2020-12-11 doc/paper/paper.tex
prepare structure with section headlines

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{FM Radio -\\Comparing HLS versus manual VHDL implementation}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The aim of this master thesis is to compare an FM radio receiver implementation in HLS versus manual VHDL. Multiple metrics, such as time effort in implementation, hardware utilization in the FPGA, or efficiency are taken into account. As a first step, the receiver structure is simulated using Matlab to evaluate different architectures and techniques to demodulate a FM radio signal. This evaluation is especially targeting a setup that requires the least possible amount of analog hardware. Once a suitable strategy is found, a prototype is implemented in hardware on a FPGA.\\
\end{abstract}

\begin{IEEEkeywords}
  Audio signal processing, FM radio frequency, FPGA, HLS, VHDL, Matlab
\end{IEEEkeywords}

@@

\section{Introduction}
% no \IEEEPARstart
This demo file is intended to serve as a ``starter file''
for IEEE conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill August 26, 2015

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
\begin{figure}[!h]
  \centering
    \includegraphics[width=2.5in]{img/fmradio-block-diagram.png}
  \caption{Block diagram of the entire system.}
  \label{fig_sim}
\end{figure}

@@

% use section* for acknowledgment
\section*{Acknowledgment}

The authors would like to thank...

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Signal Processing for Broadcast FM Radio Demodulation}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}

  %The aim of this master thesis is to compare an FM radio receiver implementation in HLS versus manual VHDL. Multiple metrics, such as time effort in implementation, hardware utilization in the FPGA, or efficiency are taken into account. As a first step, the receiver structure is simulated using Matlab to evaluate different architectures and techniques to demodulate a FM radio signal. This evaluation is especially targeting a setup that requires the least possible amount of analog hardware. Once a suitable strategy is found, a prototype is implemented in hardware on a FPGA.\\
\end{abstract}

\begin{IEEEkeywords}
%  Audio signal processing, FM radio frequency, FPGA, HLS, VHDL, Matlab
  Audio signal processing, FM radio frequency, Matlab, Simulation
\end{IEEEkeywords}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

  \subsection{Motivation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Signal Processing Theory}

  \subsection{Modulation from Baseband to RF}

  \subsection{Modulation from RF to Baseband}

  \subsection{Frequency Modulation (FM)}

  \subsection{Frequency Band}
  %may be used freely, with limited power

  \subsection{Mathematical Description of FM}

  \subsubsection{FM Channel Allocation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{FM Signal Demodulation}

  \subsection{Baseband Delay Demodulator}
  \subsection{Phase-Adapter Demodulator}
  \subsection{Phase-Locked Loop (PLL)}
  \subsection{Mixed Demodulator}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Matlab Simulation}

  \subsection{Data Acquisition}
    % RTL2832u dongle
    % Linux driver
    % IQ interleaved data stream

  \subsection{Demodulation Steps}
    \subsubsection{Recorded IF spectrum}
    \subsubsection{Modulate to FM channel center frequency}
    \subsubsection{Decimation}
    \subsubsection{Demodulation}
    \subsubsection{Verification}
      % is done subjectively only, by listening to the audio stream via a PCs' soundcard.

  % An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!h]
%  \centering
%    \includegraphics[width=2.5in]{img/fmradio-block-diagram.png}
%  \caption{Block diagram of the entire system.}
%  \label{fig_sim}
%\end{figure}

@@

% use section* for acknowledgment
% \section*{Acknowledgment}

% The authors would like to thank...
